# ABET Assessment Results for AY 2020-21

```{r echo=FALSE}
num.excelled <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=0, b2=0+0,
    c1=25, c2=8, c3=0+22, c4=25, c5=16, 
    d1=22, d2=30, d3=18, d4=0, d5=0,
    e1=0, e2=0, e3=0, e4=0, e5=0,
    f1=0, f2=34, f3=34,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=0, j2=0, j3=0, j4=0, j5=0,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.mastered <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=0, b2=0+0,
    c1=9, c2=21, c3=0+12, c4=9, c5=13, 
    d1=8, d2=4, d3=16, d4=30, d5=0,
    e1=0, e2=0, e3=0, e4=0, e5=0,
    f1=34, f2=0, f3=0,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=0, j2=0, j3=0, j4=0, j5=0,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.partially.mastered <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=0, b2=0+0,
    c1=0, c2=0, c3=0+0, c4=0, c5=5, 
    d1=4, d2=0, d3=0, d4=4, d5=34,
    e1=0, e2=0, e3=0, e4=0, e5=0,
    f1=0, f2=0, f3=0,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=0, j2=0, j3=0, j4=0, j5=0,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.below.expectations <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=0, b2=0+0,
    c1=0, c2=0, c3=0+0, c4=0, c5=0, 
    d1=0, d2=0, d3=0, d4=0, d5=0,
    e1=0, e2=0, e3=0, e4=0, e5=0,
    f1=0, f2=0, f3=0,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=0, j2=0, j3=0, j4=0, j5=0,
    k1=0, k2=0+0+0+0, k3=0, k4=0)

num.excelled['a'] <- sum(num.excelled[paste('a', 1:6, sep="")])
num.excelled['b'] <- sum(num.excelled[paste('b', 1:2, sep="")])
num.excelled['c'] <- sum(num.excelled[paste('c', 1:5, sep="")])
num.excelled['d'] <- sum(num.excelled[paste('d', 1:5, sep="")])
num.excelled['e'] <- sum(num.excelled[paste('e', 1:5, sep="")])
num.excelled['f'] <- sum(num.excelled[paste('f', 1:3, sep="")])
num.excelled['g'] <- sum(num.excelled[paste('g', 1:2, sep="")])
num.excelled['h'] <- sum(num.excelled[paste('h', 1:3, sep="")])
num.excelled['i'] <- sum(num.excelled[paste('i', 1:4, sep="")])
num.excelled['j'] <- sum(num.excelled[paste('j', 1:5, sep="")])
num.excelled['k'] <- sum(num.excelled[paste('k', 1:4, sep="")])

num.mastered['a'] <- sum(num.mastered[paste('a', 1:6, sep="")])
num.mastered['b'] <- sum(num.mastered[paste('b', 1:2, sep="")])
num.mastered['c'] <- sum(num.mastered[paste('c', 1:5, sep="")])
num.mastered['d'] <- sum(num.mastered[paste('d', 1:5, sep="")])
num.mastered['e'] <- sum(num.mastered[paste('e', 1:5, sep="")])
num.mastered['f'] <- sum(num.mastered[paste('f', 1:3, sep="")])
num.mastered['g'] <- sum(num.mastered[paste('g', 1:2, sep="")])
num.mastered['h'] <- sum(num.mastered[paste('h', 1:3, sep="")])
num.mastered['i'] <- sum(num.mastered[paste('i', 1:4, sep="")])
num.mastered['j'] <- sum(num.mastered[paste('j', 1:5, sep="")])
num.mastered['k'] <- sum(num.mastered[paste('k', 1:4, sep="")])

num.partially.mastered['a'] <- sum(num.partially.mastered[paste('a', 1:6, sep="")])
num.partially.mastered['b'] <- sum(num.partially.mastered[paste('b', 1:2, sep="")])
num.partially.mastered['c'] <- sum(num.partially.mastered[paste('c', 1:5, sep="")])
num.partially.mastered['d'] <- sum(num.partially.mastered[paste('d', 1:5, sep="")])
num.partially.mastered['e'] <- sum(num.partially.mastered[paste('e', 1:5, sep="")])
num.partially.mastered['f'] <- sum(num.partially.mastered[paste('f', 1:3, sep="")])
num.partially.mastered['g'] <- sum(num.partially.mastered[paste('g', 1:2, sep="")])
num.partially.mastered['h'] <- sum(num.partially.mastered[paste('h', 1:3, sep="")])
num.partially.mastered['i'] <- sum(num.partially.mastered[paste('i', 1:4, sep="")])
num.partially.mastered['j'] <- sum(num.partially.mastered[paste('j', 1:5, sep="")])
num.partially.mastered['k'] <- sum(num.partially.mastered[paste('k', 1:4, sep="")])

num.below.expectations['a'] <- sum(num.below.expectations[paste('a', 1:6, sep="")])
num.below.expectations['b'] <- sum(num.below.expectations[paste('b', 1:2, sep="")])
num.below.expectations['c'] <- sum(num.below.expectations[paste('c', 1:5, sep="")])
num.below.expectations['d'] <- sum(num.below.expectations[paste('d', 1:5, sep="")])
num.below.expectations['e'] <- sum(num.below.expectations[paste('e', 1:5, sep="")])
num.below.expectations['f'] <- sum(num.below.expectations[paste('f', 1:3, sep="")])
num.below.expectations['g'] <- sum(num.below.expectations[paste('g', 1:2, sep="")])
num.below.expectations['h'] <- sum(num.below.expectations[paste('h', 1:3, sep="")])
num.below.expectations['i'] <- sum(num.below.expectations[paste('i', 1:4, sep="")])
num.below.expectations['j'] <- sum(num.below.expectations[paste('j', 1:5, sep="")])
num.below.expectations['k'] <- sum(num.below.expectations[paste('k', 1:4, sep="")])

get.excelled <- function (key) {
    pct <- num.excelled[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.mastered <- function (key) {
    pct <- num.mastered[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.partially.mastered <- function (key) {
    pct <- num.partially.mastered[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.below.expectations <- function (key) {
    pct <- num.below.expectations[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
num.assessed <- function (key) {
    num <- round((num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])/4)
    return (num)
}

history.excelled <- data.frame(
    a=c(62,  45,  61, NA, NA, get.excelled('a')),
    b=c(69,  46,  34, 29, NA, get.excelled('b')),
    c=c(71,  58,  31, 54, NA, get.excelled('c')),
    d=c(66,  53,  12, 71, NA, get.excelled('d')),
    e=c(20,  98,  92, 68, 49, get.excelled('e')),
    f=c(83,  67,  22, 47, NA, get.excelled('f')),
    g=c(20, 100,  NA, NA, NA, get.excelled('g')),
    h=c(20,  81,  NA, NA, NA, get.excelled('h')),
    i=c(67,  56,  70, NA, NA, get.excelled('i')),
    j=c(79,  36,  34, 31, NA, get.excelled('j')),
    k=c(49,  74,  NA, NA, NA, get.excelled('k')))
history.mastered <- data.frame(
    a=c(10, 35,  10, NA, NA, get.mastered('a')),
    b=c(14, 33,  39, 31, NA, get.mastered('b')),
    c=c( 8, 22,  62, 46, NA, get.mastered('c')),
    d=c(17, 24,  84, 29, NA, get.mastered('d')),
    e=c(80,  2,   6, 18, 42, get.mastered('e')),
    f=c( 6, 29,  54, 53, NA, get.mastered('f')),
    g=c(80,  0,  NA, NA, NA, get.mastered('g')),
    h=c(80, 10,  NA, NA, NA, get.mastered('h')),
    i=c(24, 26,  23, NA, NA, get.mastered('i')),
    j=c(15, 26,  17, 22, NA, get.mastered('j')),
    k=c(15,  8,  NA, NA, NA, get.mastered('k')))
history.partially.mastered <- data.frame(
    a=c(12,  9,  12, NA, NA, get.partially.mastered('a')),
    b=c(10, 15,   7, 31, NA, get.partially.mastered('b')),
    c=c(11,  9,   4,  0, NA, get.partially.mastered('c')),
    d=c( 7, 19,   3,  0, NA, get.partially.mastered('d')),
    e=c( 0,  0,   0, 12,  8, get.partially.mastered('e')),
    f=c(11,  4,  21,  0, NA, get.partially.mastered('f')),
    g=c( 0,  0,  NA, NA, NA, get.partially.mastered('g')),
    h=c( 0,  9,  NA, NA, NA, get.partially.mastered('h')),
    i=c( 3, 10,   2, NA, NA, get.partially.mastered('i')),
    j=c( 2, 17,  31, 28, NA, get.partially.mastered('j')),
    k=c(24,  2,  NA, NA, NA, get.partially.mastered('k')))
history.below.expectations <- data.frame(
    a=c(16, 11,  18, NA, NA, get.below.expectations('a')),
    b=c( 7,  6,  20,  9, NA, get.below.expectations('b')),
    c=c(10, 11,   3,  0, NA, get.below.expectations('c')),
    d=c(10,  4,   1,  1, NA, get.below.expectations('d')),
    e=c( 0,  0,   2,  0,  2, get.below.expectations('e')),
    f=c( 0,  0,   2,  0, NA, get.below.expectations('f')),
    g=c( 0,  0,  NA, NA, NA, get.below.expectations('g')),
    h=c( 0,  0,  NA, NA, NA, get.below.expectations('h')),
    i=c( 6,  7,   5, NA, NA, get.below.expectations('i')),
    j=c( 4, 21,  18, 19, NA, get.below.expectations('j')),
    k=c(12, 16,  NA, NA, NA, get.below.expectations('k')))

history.pass <- history.excelled + history.mastered
history.fail <- history.partially.mastered + history.below.expectations

penultimate.value <- function(df, colidx) {
  nr = nrow(df) - 1
  while (nr > 0) {
    if (!is.na(df[nr,colidx])) {
      return (df[nr,colidx])
    }
    nr <- nr - 1
  }
  return (NA)
}
```

## Summary

The data for AY 2019-20 was used as part of our continuing improvement process
in the Fall of 2021.

Outcome  | % Excelled | % Mastered | % Partially Mastered | % Below Expectations | #Student Assessments
:-------:|-----------:|-----------:|---------------------:|---------------------:|------------------------:
(1)      | `r get.excelled('b')` | `r get.mastered('b')` | `r get.partially.mastered('b')` | `r get.below.expectations('b')` | `r num.assessed('b')`
(2)      | `r get.excelled('c')` | `r get.mastered('c')` | `r get.partially.mastered('c')` | `r get.below.expectations('c')` | `r num.assessed('c')`
(3)      | `r get.excelled('f')` | `r get.mastered('f')` | `r get.partially.mastered('f')` | `r get.below.expectations('f')` | `r num.assessed('f')`
(4)      | `r get.excelled('e')` | `r get.mastered('e')` | `r get.partially.mastered('e')` | `r get.below.expectations('e')` | `r num.assessed('e')`
(5)      | `r get.excelled('d')` | `r get.mastered('d')` | `r get.partially.mastered('d')` | `r get.below.expectations('d')` | `r num.assessed('d')`
(6)      | `r get.excelled('j')` | `r get.mastered('j')` | `r get.partially.mastered('j')` | `r get.below.expectations('j')` | `r num.assessed('j')`

Considering Excelled and Mastered to "Satisfy" each student outcome, we can look at historical trends.

Outcome | %Satisfied 2014-15       | %Satisfied 2015-16       | %Satisfied 2016-17       | %Satisfied 2018-19       | %Satisfied 2019-20       | %Satisfied 2020-21       | Last Year Change
:------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-----------------------:
(1)     | `r history.pass[1, 'b']` | `r history.pass[2, 'b']` | `r history.pass[3, 'b']` | `r history.pass[4, 'b']` | `r history.pass[5, 'b']` | `r history.pass[6, 'b']` | `r history.pass[6, 'b'] - penultimate.value(history.pass, 'b')`
(2)     | `r history.pass[1, 'c']` | `r history.pass[2, 'c']` | `r history.pass[3, 'c']` | `r history.pass[4, 'c']` | `r history.pass[5, 'c']` | `r history.pass[6, 'c']` | `r history.pass[6, 'c'] - penultimate.value(history.pass, 'c')`
(3)     | `r history.pass[1, 'f']` | `r history.pass[2, 'f']` | `r history.pass[3, 'f']` | `r history.pass[4, 'f']` | `r history.pass[5, 'f']` | `r history.pass[6, 'f']` | `r history.pass[6, 'f'] - penultimate.value(history.pass, 'f')`
(4)     | `r history.pass[1, 'e']` | `r history.pass[2, 'e']` | `r history.pass[3, 'e']` | `r history.pass[4, 'e']` | `r history.pass[5, 'e']` | `r history.pass[6, 'e']` | `r history.pass[6, 'e'] - penultimate.value(history.pass, 'e')`
(5)     | `r history.pass[1, 'd']` | `r history.pass[2, 'd']` | `r history.pass[3, 'd']` | `r history.pass[4, 'd']` | `r history.pass[5, 'd']` | `r history.pass[6, 'd']` | `r history.pass[6, 'd'] - penultimate.value(history.pass, 'd')`
(6)     | `r history.pass[1, 'j']` | `r history.pass[2, 'j']` | `r history.pass[3, 'j']` | `r history.pass[4, 'j']` | `r history.pass[5, 'j']` | `r history.pass[6, 'j']` | `r history.pass[6, 'j'] - penultimate.value(history.pass, 'j')`

The following graphs show the history of the outcomes (1) through (6), using data from the old outcomes (a)-(k) for prior years.

```{r fig.width=10, fig.height=8, echo=FALSE, cache=FALSE}

years <- c(2015, 2016, 2017, 2019, 2020, 2021)
year_labels = c('2014-15', '2015-16', '2016-17', '2018-19', '2019-20', '2020-21')
outcome_map=c('b', 'c', 'f', 'e', 'd', 'j')
for (idx in c(1, 2, 3, 4, 5, 6)) {
  # png(paste("outcome-", idx, ".png", sep=""))
  outcome = outcome_map[idx]
  hist <- c(history.pass[1, outcome], history.pass[2, outcome], history.pass[3, outcome], history.pass[4, outcome], history.pass[5, outcome], history.pass[6, outcome])
  plot(years, hist, xaxt="n", ylim=c(40,100))
  abline(h=80, lty=3)
  lines(approx(years, hist, c(2015, 2016, 2017, 2019, 2020, 2021)))
  axis(side=1, at=years, labels=year_labels)
  title(paste('Outcome (',  idx, ')', sep=""))
  # dev.off()
}

```

More details of student assessment can be seen by considering the assessment of individual PKIs.

Outcome | KPI    | % Excelled | % Mastered | % Partially Mastered | % Below Expectations | #Student Assessments
:------:|:------:|-----------:|-----------:|---------------------:|---------------------:|--------------------:
(1)     | (1.1)  |  `r get.excelled('b1')` | `r get.mastered('b1')` | `r get.partially.mastered('b1')` | `r get.below.expectations('b1')` | `r num.assessed('b1')`
&nbsp;  | (1.2)  |  `r get.excelled('b2')` | `r get.mastered('b2')` | `r get.partially.mastered('b2')` | `r get.below.expectations('b2')` | `r num.assessed('b2')`
(2)     | (2.1)  |  `r get.excelled('c1')` | `r get.mastered('c1')` | `r get.partially.mastered('c1')` | `r get.below.expectations('c1')` | `r num.assessed('c1')`
&nbsp;  | (2.2)  |  `r get.excelled('c2')` | `r get.mastered('c2')` | `r get.partially.mastered('c2')` | `r get.below.expectations('c2')` | `r num.assessed('c2')`
&nbsp;  | (2.3)  |  `r get.excelled('c3')` | `r get.mastered('c3')` | `r get.partially.mastered('c3')` | `r get.below.expectations('c3')` | `r num.assessed('c3')`
&nbsp;  | (2.4)  |  `r get.excelled('c4')` | `r get.mastered('c4')` | `r get.partially.mastered('c4')` | `r get.below.expectations('c4')` | `r num.assessed('c4')`
&nbsp;  | (2.5)  |  `r get.excelled('c5')` | `r get.mastered('c5')` | `r get.partially.mastered('c5')` | `r get.below.expectations('c5')` | `r num.assessed('c5')`
(3)     | (3.1)  |  `r get.excelled('f1')` | `r get.mastered('f1')` | `r get.partially.mastered('f1')` | `r get.below.expectations('f1')` | `r num.assessed('f1')`
&nbsp;  | (3.2)  |  `r get.excelled('f2')` | `r get.mastered('f2')` | `r get.partially.mastered('f2')` | `r get.below.expectations('f2')` | `r num.assessed('f2')`
&nbsp;  | (3.3)  |  `r get.excelled('f3')` | `r get.mastered('f3')` | `r get.partially.mastered('f3')` | `r get.below.expectations('f3')` | `r num.assessed('f3')`
(4)     | (4.1)  |  `r get.excelled('e1')` | `r get.mastered('e1')` | `r get.partially.mastered('e1')` | `r get.below.expectations('e1')` | `r num.assessed('e1')`
&nbsp;  | (4.2)  |  `r get.excelled('e2')` | `r get.mastered('e2')` | `r get.partially.mastered('e2')` | `r get.below.expectations('e2')` | `r num.assessed('e2')`
&nbsp;  | (4.3)  |  `r get.excelled('e3')` | `r get.mastered('e3')` | `r get.partially.mastered('e3')` | `r get.below.expectations('e3')` | `r num.assessed('e3')`
&nbsp;  | (4.4)  |  `r get.excelled('e4')` | `r get.mastered('e4')` | `r get.partially.mastered('e4')` | `r get.below.expectations('e4')` | `r num.assessed('e4')`
&nbsp;  | (4.5)  |  `r get.excelled('e5')` | `r get.mastered('e5')` | `r get.partially.mastered('e5')` | `r get.below.expectations('e5')` | `r num.assessed('e5')`
(5)     | (5.1)  |  `r get.excelled('d1')` | `r get.mastered('d1')` | `r get.partially.mastered('d1')` | `r get.below.expectations('d1')` | `r num.assessed('d1')`
&nbsp;  | (5.2)  |  `r get.excelled('d2')` | `r get.mastered('d2')` | `r get.partially.mastered('d2')` | `r get.below.expectations('d2')` | `r num.assessed('d2')`
&nbsp;  | (5.3)  |  `r get.excelled('d3')` | `r get.mastered('d3')` | `r get.partially.mastered('d3')` | `r get.below.expectations('d3')` | `r num.assessed('d3')`
&nbsp;  | (5.4)  |  `r get.excelled('d4')` | `r get.mastered('d4')` | `r get.partially.mastered('d4')` | `r get.below.expectations('d4')` | `r num.assessed('d4')`
&nbsp;  | (5.5)  |  `r get.excelled('d5')` | `r get.mastered('d5')` | `r get.partially.mastered('d5')` | `r get.below.expectations('d5')` | `r num.assessed('d5')`
(6)     | (6.1)  |  `r get.excelled('j1')` | `r get.mastered('j1')` | `r get.partially.mastered('j1')` | `r get.below.expectations('j1')` | `r num.assessed('j1')`
&nbsp;  | (6.2)  |  `r get.excelled('j2')` | `r get.mastered('j2')` | `r get.partially.mastered('j2')` | `r get.below.expectations('j2')` | `r num.assessed('j2')`
&nbsp;  | (6.3)  |  `r get.excelled('j3')` | `r get.mastered('j3')` | `r get.partially.mastered('j3')` | `r get.below.expectations('j3')` | `r num.assessed('j3')`
&nbsp;  | (6.4)  |  `r get.excelled('j4')` | `r get.mastered('j4')` | `r get.partially.mastered('j4')` | `r get.below.expectations('j4')` | `r num.assessed('j4')`
&nbsp;  | (6.5)  |  `r get.excelled('j5')` | `r get.mastered('j5')` | `r get.partially.mastered('j5')` | `r get.below.expectations('j5')` | `r num.assessed('j5')`

## Assessment Data

### COSC 3020: Algorithms & Data Structures, Lars Kotthoff MISSING

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 3020: Algorithms & Data Structures | Every other year, starting 2016-17

---

    Performance Indicator (a.4): Calculate the sum of arithmetic series 
                                 that arise in computing applications
 

---

    Performance Indicator (a.5): Calculate the sum of geometric series 
                                 that arise in computing applications
 

---

    Performance Indicator (a.6) :  Use calculus to find the asymptotic limit of functions


---

    Performance Indicator (b.1) :  Identify key components and algorithms necessary for a solution

    Assignment 3: Implement two algorithms for solving the traveling salesman 
    problem and compare them. 

    34 students assessed. 

    10 students excelled. 
    9 students mastered. 
    4 students partially mastered. 
    11 students were below expectations. 

---

    Performance Indicator (b.2) :  Analyze at two or more proposed solutions to a given problem and select the best solution for the given problem 

    Assignment 3: Implement two algorithms for solving the traveling salesman 
    problem and compare them. 

    34 students assessed. 

    10 students excelled. 
    9 students mastered. 
    4 students partially mastered. 
    11 students were below expectations. 

---

    Performance Indicator (j.1) :  Analyze the asymptotic cost of divide-and-conquer algorithms

    Question 3 in assignment 2: Implement an iterative and in-place version of merge 
    sort and analyze its complexity. 

    31 students assessed. 

    4 students excelled. 
    5 students mastered. 
    14 students partially mastered. 
    8 students were below expectations. 

---

    Performance Indicator (j.2) :  Analyze the asymptotic cost of recursive algorithms

    Question 3 in the midterm: Give Theta-bounds for three recurrence 
    relations. 

    33 students assessed. 

    13 students excelled. 
    8 students mastered. 
    12 students partially mastered. 
    0 students were below expectations. 

---

    Performance Indicator (j.3): Analyze the asymptotic cost of basic graph algorithms

    Lab 7: Implement the Floyd-Warshall algorithm and analyze its complexity. 

    34 students assessed. 

    24 students excelled. 
    8 students mastered. 
    2 students were below expectations. 

---

    Performance Indicator (j.4):  Describe the impact of techniques such as caching 
    and dynamic programming on the performance of algorithms

    Question 5 in final: Implement a dynamic programming solution to 
    compute the Liouville number. 

    33 students assessed. 

    3 students excelled. 
    2 students mastered. 
    20 students partially mastered. 
    8 students were below expectations. 

---

    Performance Indicator (j.5):  Understand the difference between polynomial 
    and exponential complexity

    Assignment 3: Implement two algorithms for solving the traveling salesman 
    problem (one complete, exponential complexity, one approximate, polynomial 
    complexity) and compare them. 

    34 students assessed. 

    10 students excelled. 
    9 students mastered. 
    4 students partially mastered. 
    11 students were below expectations. 

### COSC 4950/5: Senior Design I & II, Mike Borowczak

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 4950: Senior Design I              | Every other year, starting 2017-18
COSC 4955: Senior Design II             | Every other year, starting 2017-18

This is the capstone course. Students work in groups ranging from 3 to 5, 
select a project, and create a software system to solve it. The
students flesh out the project ideas, deciding on the important features
and trying to come to terms with project risk.  They decide what technology
to use, and they proceed to implementation.  They also document their
decisions by writing use cases, or other tools as appropriate (e.g., 
story boards for projects that choose to write games).

Classtime is devoted to group work and presentations that updated the 
instructor and the other teams on the status of the project. They also
create a poster presentation of their project and do a final presentation
to a wide audience. The class presentations, poster, and final presentations
are the main tools used for assessment.

    Performance Indicator (2.1): Identify constraints on the design problem

    Does the capstone Project Design Document contain details on constraint (e.g. limitations, and feasiblity)

    34 students were assessed.

    25 students excelled.
    9 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.2): Establish acceptance criteria for a solution

    Does the capstone Project Design Document contain acceptence criteria (e.g. gated design/acceptance criteria)?

    34 students were assessed.

    8 students excelled.
    21 students mastered.
    5 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.3): Design the selected solution for a given problem

    Mid-capstone presentation and github respositories contain evidence of design

    34 students were assessed.

    22 students excelled.
    12 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.4): Implement the designed solution for a given problem

    Capstone presentation and github respositories contain evidence of deliverables

    34 students were assessed.

    25 students excelled.
    9 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.5): Evaluate the implemented solution

    Mid-capstone presentation: Pathforward,  Evaluation of other designs

    34 students were assessed.

    16 students excelled.
    13 students mastered.
    5 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.1): Listen to other team members

    End of capstone team reflection.

    34 students were assessed.

    22 students excelled.
    8 students mastered.
    4 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.2): Actively discuss team projects, objectives, or challenges with other team members

    Actively discuss team projects, objectives, or challenges with other team members

    34 students were assessed.

    30 students excelled.
    4 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.3): Fulfill team duties on time

    Fulfill team duties on time

    34 students were assessed.

    18 students excelled.
    16 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.4): Share in the work of the team

    Status Updates; Git Tracking (does statement of responsibilities align to actual work performed)

    34 students were assessed.

    30 students excelled.
    4 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.5): Research and gather information

    Capstone Project Design Document

    34 students were assessed.

    0 students excelled.
    34 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (3.1): Write technical reports

    Is the Capstone Project Design Document written for a technical audience?

    34 students were assessed.

    0 students excelled.
    34 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (3.2): Present technical material to technical peers

    Capstone presentation survey tool: did peers understand the presentation?

    34 students were assessed.

    34 students excelled.
    0 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (3.3): Present technical material to non-technical visitors

    Capstone presentation survey tool: did non-technical visitors understand the presentation?

    34 students were assessed.

    34 students excelled.
    0 students mastered.
    0 students partially mastered.
    0 students were below expectations.

