# ABET Assessment Results for AY 2020-21

```{r echo=FALSE}
num.excelled <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=11, b2=23+8,
    c1=37, c2=37, c3=23+37, c4=37, c5=36, 
    d1=30, d2=37, d3=29, d4=29, d5=29,
    e1=14, e2=0, e3=0, e4=14, e5=0,
    f1=33, f2=31, f3=31,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=8, j2=8, j3=7, j4=18, j5=9,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.mastered <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=13, b2=24+1,
    c1=3, c2=3, c3=24+3, c4=3, c5=3, 
    d1=7, d2=7, d3=6, d4=6, d5=5,
    e1=4, e2=0, e3=0, e4=4, e5=0,
    f1=3, f2=5, f3=5,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=16, j2=12, j3=5, j4=6, j5=9,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.partially.mastered <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=2, b2=0+3,
    c1=0, c2=0, c3=2+0, c4=0, c5=0, 
    d1=0, d2=0, d3=2, d4=2, d5=3,
    e1=2, e2=0, e3=0, e4=2, e5=0,
    f1=0, f2=0, f3=0,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=4, j2=6, j3=0, j4=1, j5=6,
    k1=0, k2=0+0+0+0, k3=0, k4=0)
num.below.expectations <- c(
    a1=0+0, a2=0, a3=0, a4=0, a5=0, a6=0,
    b1=3, b2=4+14,
    c1=0, c2=0, c3=2+0, c4=0, c5=1, 
    d1=0, d2=0, d3=0, d4=0, d5=0,
    e1=1, e2=0, e3=0, e4=1, e5=0,
    f1=1, f2=1, f3=1,
    g1=0, g2=0,
    h1=0, h2=0, h3=0,
    i1=0, i2=0, i3=0, i4=0,
    j1=1, j2=3, j3=6, j4=2, j5=4,
    k1=0, k2=0+0+0+0, k3=0, k4=0)

num.excelled['a'] <- sum(num.excelled[paste('a', 1:6, sep="")])
num.excelled['b'] <- sum(num.excelled[paste('b', 1:2, sep="")])
num.excelled['c'] <- sum(num.excelled[paste('c', 1:5, sep="")])
num.excelled['d'] <- sum(num.excelled[paste('d', 1:5, sep="")])
num.excelled['e'] <- sum(num.excelled[paste('e', 1:5, sep="")])
num.excelled['f'] <- sum(num.excelled[paste('f', 1:3, sep="")])
num.excelled['g'] <- sum(num.excelled[paste('g', 1:2, sep="")])
num.excelled['h'] <- sum(num.excelled[paste('h', 1:3, sep="")])
num.excelled['i'] <- sum(num.excelled[paste('i', 1:4, sep="")])
num.excelled['j'] <- sum(num.excelled[paste('j', 1:5, sep="")])
num.excelled['k'] <- sum(num.excelled[paste('k', 1:4, sep="")])

num.mastered['a'] <- sum(num.mastered[paste('a', 1:6, sep="")])
num.mastered['b'] <- sum(num.mastered[paste('b', 1:2, sep="")])
num.mastered['c'] <- sum(num.mastered[paste('c', 1:5, sep="")])
num.mastered['d'] <- sum(num.mastered[paste('d', 1:5, sep="")])
num.mastered['e'] <- sum(num.mastered[paste('e', 1:5, sep="")])
num.mastered['f'] <- sum(num.mastered[paste('f', 1:3, sep="")])
num.mastered['g'] <- sum(num.mastered[paste('g', 1:2, sep="")])
num.mastered['h'] <- sum(num.mastered[paste('h', 1:3, sep="")])
num.mastered['i'] <- sum(num.mastered[paste('i', 1:4, sep="")])
num.mastered['j'] <- sum(num.mastered[paste('j', 1:5, sep="")])
num.mastered['k'] <- sum(num.mastered[paste('k', 1:4, sep="")])

num.partially.mastered['a'] <- sum(num.partially.mastered[paste('a', 1:6, sep="")])
num.partially.mastered['b'] <- sum(num.partially.mastered[paste('b', 1:2, sep="")])
num.partially.mastered['c'] <- sum(num.partially.mastered[paste('c', 1:5, sep="")])
num.partially.mastered['d'] <- sum(num.partially.mastered[paste('d', 1:5, sep="")])
num.partially.mastered['e'] <- sum(num.partially.mastered[paste('e', 1:5, sep="")])
num.partially.mastered['f'] <- sum(num.partially.mastered[paste('f', 1:3, sep="")])
num.partially.mastered['g'] <- sum(num.partially.mastered[paste('g', 1:2, sep="")])
num.partially.mastered['h'] <- sum(num.partially.mastered[paste('h', 1:3, sep="")])
num.partially.mastered['i'] <- sum(num.partially.mastered[paste('i', 1:4, sep="")])
num.partially.mastered['j'] <- sum(num.partially.mastered[paste('j', 1:5, sep="")])
num.partially.mastered['k'] <- sum(num.partially.mastered[paste('k', 1:4, sep="")])

num.below.expectations['a'] <- sum(num.below.expectations[paste('a', 1:6, sep="")])
num.below.expectations['b'] <- sum(num.below.expectations[paste('b', 1:2, sep="")])
num.below.expectations['c'] <- sum(num.below.expectations[paste('c', 1:5, sep="")])
num.below.expectations['d'] <- sum(num.below.expectations[paste('d', 1:5, sep="")])
num.below.expectations['e'] <- sum(num.below.expectations[paste('e', 1:5, sep="")])
num.below.expectations['f'] <- sum(num.below.expectations[paste('f', 1:3, sep="")])
num.below.expectations['g'] <- sum(num.below.expectations[paste('g', 1:2, sep="")])
num.below.expectations['h'] <- sum(num.below.expectations[paste('h', 1:3, sep="")])
num.below.expectations['i'] <- sum(num.below.expectations[paste('i', 1:4, sep="")])
num.below.expectations['j'] <- sum(num.below.expectations[paste('j', 1:5, sep="")])
num.below.expectations['k'] <- sum(num.below.expectations[paste('k', 1:4, sep="")])

get.excelled <- function (key) {
    pct <- num.excelled[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.mastered <- function (key) {
    pct <- num.mastered[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.partially.mastered <- function (key) {
    pct <- num.partially.mastered[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
get.below.expectations <- function (key) {
    pct <- num.below.expectations[[key]] / (num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]])
    if (is.nan(pct)) {
      pct = NA
    }
    return (round(100*pct))
}
num.assessed <- function (key) {
    num <- round((num.excelled[[key]] + num.mastered[[key]] + num.partially.mastered[[key]] + num.below.expectations[[key]]))
    return (num)
}

history.excelled <- data.frame(
    a=c(62,  45,  61, NA, NA, NA, get.excelled('a')),
    b=c(69,  46,  34, 29, NA, NA, get.excelled('b')),
    c=c(71,  58,  31, 54, NA, 58, get.excelled('c')),
    d=c(66,  53,  12, 71, NA, 41, get.excelled('d')),
    e=c(20,  98,  92, 68, 49, NA, get.excelled('e')),
    f=c(83,  67,  22, 47, NA, 67, get.excelled('f')),
    g=c(20, 100,  NA, NA, NA, NA, get.excelled('g')),
    h=c(20,  81,  NA, NA, NA, NA, get.excelled('h')),
    i=c(67,  56,  70, NA, NA, NA, get.excelled('i')),
    j=c(79,  36,  34, 31, NA, NA, get.excelled('j')),
    k=c(49,  74,  NA, NA, NA, NA, get.excelled('k')))
history.mastered <- data.frame(
    a=c(10, 35,  10, NA, NA, NA, get.mastered('a')),
    b=c(14, 33,  39, 31, NA, NA, get.mastered('b')),
    c=c( 8, 22,  62, 46, NA, 39, get.mastered('c')),
    d=c(17, 24,  84, 29, NA, 34, get.mastered('d')),
    e=c(80,  2,   6, 18, 42, NA, get.mastered('e')),
    f=c( 6, 29,  54, 53, NA, 33, get.mastered('f')),
    g=c(80,  0,  NA, NA, NA, NA, get.mastered('g')),
    h=c(80, 10,  NA, NA, NA, NA, get.mastered('h')),
    i=c(24, 26,  23, NA, NA, NA, get.mastered('i')),
    j=c(15, 26,  17, 22, NA, NA, get.mastered('j')),
    k=c(15,  8,  NA, NA, NA, NA, get.mastered('k')))
history.partially.mastered <- data.frame(
    a=c(12,  9,  12, NA, NA, NA, get.partially.mastered('a')),
    b=c(10, 15,   7, 31, NA, NA, get.partially.mastered('b')),
    c=c(11,  9,   4,  0, NA,  3, get.partially.mastered('c')),
    d=c( 7, 19,   3,  0, NA, 25, get.partially.mastered('d')),
    e=c( 0,  0,   0, 12,  8, NA, get.partially.mastered('e')),
    f=c(11,  4,  21,  0, NA,  0, get.partially.mastered('f')),
    g=c( 0,  0,  NA, NA, NA, NA, get.partially.mastered('g')),
    h=c( 0,  9,  NA, NA, NA, NA, get.partially.mastered('h')),
    i=c( 3, 10,   2, NA, NA, NA, get.partially.mastered('i')),
    j=c( 2, 17,  31, 28, NA, NA, get.partially.mastered('j')),
    k=c(24,  2,  NA, NA, NA, NA, get.partially.mastered('k')))
history.below.expectations <- data.frame(
    a=c(16, 11,  18, NA, NA, NA, get.below.expectations('a')),
    b=c( 7,  6,  20,  9, NA, NA, get.below.expectations('b')),
    c=c(10, 11,   3,  0, NA,  0, get.below.expectations('c')),
    d=c(10,  4,   1,  1, NA,  0, get.below.expectations('d')),
    e=c( 0,  0,   2,  0,  2, NA, get.below.expectations('e')),
    f=c( 0,  0,   2,  0, NA,  0, get.below.expectations('f')),
    g=c( 0,  0,  NA, NA, NA, NA, get.below.expectations('g')),
    h=c( 0,  0,  NA, NA, NA, NA, get.below.expectations('h')),
    i=c( 6,  7,   5, NA, NA, NA, get.below.expectations('i')),
    j=c( 4, 21,  18, 19, NA, NA, get.below.expectations('j')),
    k=c(12, 16,  NA, NA, NA, NA, get.below.expectations('k')))

history.pass <- history.excelled + history.mastered
history.fail <- history.partially.mastered + history.below.expectations

penultimate.value <- function(df, colidx) {
  nr = nrow(df) - 1
  while (nr > 0) {
    if (!is.na(df[nr,colidx])) {
      return (df[nr,colidx])
    }
    nr <- nr - 1
  }
  return (NA)
}
```

## Summary

The data for AY 2019-20 was used as part of our continuing improvement process
in the Fall of 2021.

Outcome  | % Excelled | % Mastered | % Partially Mastered | % Below Expectations | #Student Assessments
:-------:|-----------:|-----------:|---------------------:|---------------------:|------------------------:
(1)      | `r get.excelled('b')` | `r get.mastered('b')` | `r get.partially.mastered('b')` | `r get.below.expectations('b')` | `r num.assessed('b')`
(2)      | `r get.excelled('c')` | `r get.mastered('c')` | `r get.partially.mastered('c')` | `r get.below.expectations('c')` | `r num.assessed('c')`
(3)      | `r get.excelled('f')` | `r get.mastered('f')` | `r get.partially.mastered('f')` | `r get.below.expectations('f')` | `r num.assessed('f')`
(4)      | `r get.excelled('e')` | `r get.mastered('e')` | `r get.partially.mastered('e')` | `r get.below.expectations('e')` | `r num.assessed('e')`
(5)      | `r get.excelled('d')` | `r get.mastered('d')` | `r get.partially.mastered('d')` | `r get.below.expectations('d')` | `r num.assessed('d')`
(6)      | `r get.excelled('j')` | `r get.mastered('j')` | `r get.partially.mastered('j')` | `r get.below.expectations('j')` | `r num.assessed('j')`

Considering Excelled and Mastered to "Satisfy" each student outcome, we can look at historical trends.

Outcome | %Satisfied 2014-15       | %Satisfied 2015-16       | %Satisfied 2016-17       | %Satisfied 2018-19       | %Satisfied 2019-20       | %Satisfied 2020-21       | %Satisfied 2023-24       | Last Year Change
:------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-------------------------:|-----------------------:
(1)     | `r history.pass[1, 'b']` | `r history.pass[2, 'b']` | `r history.pass[3, 'b']` | `r history.pass[4, 'b']` | `r history.pass[5, 'b']` | `r history.pass[6, 'b']` | `r history.pass[6, 'b'] - penultimate.value(history.pass, 'b')`
(2)     | `r history.pass[1, 'c']` | `r history.pass[2, 'c']` | `r history.pass[3, 'c']` | `r history.pass[4, 'c']` | `r history.pass[5, 'c']` | `r history.pass[6, 'c']` | `r history.pass[6, 'c'] - penultimate.value(history.pass, 'c')`
(3)     | `r history.pass[1, 'f']` | `r history.pass[2, 'f']` | `r history.pass[3, 'f']` | `r history.pass[4, 'f']` | `r history.pass[5, 'f']` | `r history.pass[6, 'f']` | `r history.pass[6, 'f'] - penultimate.value(history.pass, 'f')`
(4)     | `r history.pass[1, 'e']` | `r history.pass[2, 'e']` | `r history.pass[3, 'e']` | `r history.pass[4, 'e']` | `r history.pass[5, 'e']` | `r history.pass[6, 'e']` | `r history.pass[6, 'e'] - penultimate.value(history.pass, 'e')`
(5)     | `r history.pass[1, 'd']` | `r history.pass[2, 'd']` | `r history.pass[3, 'd']` | `r history.pass[4, 'd']` | `r history.pass[5, 'd']` | `r history.pass[6, 'd']` | `r history.pass[6, 'd'] - penultimate.value(history.pass, 'd')`
(6)     | `r history.pass[1, 'j']` | `r history.pass[2, 'j']` | `r history.pass[3, 'j']` | `r history.pass[4, 'j']` | `r history.pass[5, 'j']` | `r history.pass[6, 'j']` | `r history.pass[6, 'j'] - penultimate.value(history.pass, 'j')`

The following graphs show the history of the outcomes (1) through (6), using data from the old outcomes (a)-(k) for prior years.

```{r fig.width=10, fig.height=8, echo=FALSE, cache=FALSE}

years <- c(2015, 2016, 2017, 2019, 2020, 2021, 2024)
year_labels = c('2014-15', '2015-16', '2016-17', '2018-19', '2019-20', '2020-21', '2023-24')
outcome_map=c('b', 'c', 'f', 'e', 'd', 'j')
for (idx in c(1, 2, 3, 4, 5, 6)) {
  # png(paste("outcome-", idx, ".png", sep=""))
  outcome = outcome_map[idx]
  hist <- c(history.pass[1, outcome], history.pass[2, outcome], history.pass[3, outcome], history.pass[4, outcome], history.pass[5, outcome], history.pass[6, outcome], history.pass[7, outcome])
  plot(years, hist, xaxt="n", ylim=c(40,100))
  abline(h=80, lty=3) 
  lines(approx(years, hist, c(2015, 2016, 2017, 2019, 2020, 2021, 2024)))
  axis(side=1, at=years, labels=year_labels)
  title(paste('Outcome (',  idx, ')', sep=""))
  # dev.off()
}

```

More details of student assessment can be seen by considering the assessment of individual PKIs.

Outcome | KPI    | % Excelled | % Mastered | % Partially Mastered | % Below Expectations | #Student Assessments
:------:|:------:|-----------:|-----------:|---------------------:|---------------------:|--------------------:
(1)     | (1.1)  |  `r get.excelled('b1')` | `r get.mastered('b1')` | `r get.partially.mastered('b1')` | `r get.below.expectations('b1')` | `r num.assessed('b1')`
&nbsp;  | (1.2)  |  `r get.excelled('b2')` | `r get.mastered('b2')` | `r get.partially.mastered('b2')` | `r get.below.expectations('b2')` | `r num.assessed('b2')`
(2)     | (2.1)  |  `r get.excelled('c1')` | `r get.mastered('c1')` | `r get.partially.mastered('c1')` | `r get.below.expectations('c1')` | `r num.assessed('c1')`
&nbsp;  | (2.2)  |  `r get.excelled('c2')` | `r get.mastered('c2')` | `r get.partially.mastered('c2')` | `r get.below.expectations('c2')` | `r num.assessed('c2')`
&nbsp;  | (2.3)  |  `r get.excelled('c3')` | `r get.mastered('c3')` | `r get.partially.mastered('c3')` | `r get.below.expectations('c3')` | `r num.assessed('c3')`
&nbsp;  | (2.4)  |  `r get.excelled('c4')` | `r get.mastered('c4')` | `r get.partially.mastered('c4')` | `r get.below.expectations('c4')` | `r num.assessed('c4')`
&nbsp;  | (2.5)  |  `r get.excelled('c5')` | `r get.mastered('c5')` | `r get.partially.mastered('c5')` | `r get.below.expectations('c5')` | `r num.assessed('c5')`
(3)     | (3.1)  |  `r get.excelled('f1')` | `r get.mastered('f1')` | `r get.partially.mastered('f1')` | `r get.below.expectations('f1')` | `r num.assessed('f1')`
&nbsp;  | (3.2)  |  `r get.excelled('f2')` | `r get.mastered('f2')` | `r get.partially.mastered('f2')` | `r get.below.expectations('f2')` | `r num.assessed('f2')`
&nbsp;  | (3.3)  |  `r get.excelled('f3')` | `r get.mastered('f3')` | `r get.partially.mastered('f3')` | `r get.below.expectations('f3')` | `r num.assessed('f3')`
(4)     | (4.1)  |  `r get.excelled('e1')` | `r get.mastered('e1')` | `r get.partially.mastered('e1')` | `r get.below.expectations('e1')` | `r num.assessed('e1')`
&nbsp;  | (4.2)  |  `r get.excelled('e2')` | `r get.mastered('e2')` | `r get.partially.mastered('e2')` | `r get.below.expectations('e2')` | `r num.assessed('e2')`
&nbsp;  | (4.3)  |  `r get.excelled('e3')` | `r get.mastered('e3')` | `r get.partially.mastered('e3')` | `r get.below.expectations('e3')` | `r num.assessed('e3')`
&nbsp;  | (4.4)  |  `r get.excelled('e4')` | `r get.mastered('e4')` | `r get.partially.mastered('e4')` | `r get.below.expectations('e4')` | `r num.assessed('e4')`
(5)     | (5.1)  |  `r get.excelled('d1')` | `r get.mastered('d1')` | `r get.partially.mastered('d1')` | `r get.below.expectations('d1')` | `r num.assessed('d1')`
&nbsp;  | (5.2)  |  `r get.excelled('d2')` | `r get.mastered('d2')` | `r get.partially.mastered('d2')` | `r get.below.expectations('d2')` | `r num.assessed('d2')`
&nbsp;  | (5.3)  |  `r get.excelled('d3')` | `r get.mastered('d3')` | `r get.partially.mastered('d3')` | `r get.below.expectations('d3')` | `r num.assessed('d3')`
&nbsp;  | (5.4)  |  `r get.excelled('d4')` | `r get.mastered('d4')` | `r get.partially.mastered('d4')` | `r get.below.expectations('d4')` | `r num.assessed('d4')`
&nbsp;  | (5.5)  |  `r get.excelled('d5')` | `r get.mastered('d5')` | `r get.partially.mastered('d5')` | `r get.below.expectations('d5')` | `r num.assessed('d5')`
(6)     | (6.1)  |  `r get.excelled('j1')` | `r get.mastered('j1')` | `r get.partially.mastered('j1')` | `r get.below.expectations('j1')` | `r num.assessed('j1')`
&nbsp;  | (6.2)  |  `r get.excelled('j2')` | `r get.mastered('j2')` | `r get.partially.mastered('j2')` | `r get.below.expectations('j2')` | `r num.assessed('j2')`
&nbsp;  | (6.3)  |  `r get.excelled('j3')` | `r get.mastered('j3')` | `r get.partially.mastered('j3')` | `r get.below.expectations('j3')` | `r num.assessed('j3')`
&nbsp;  | (6.4)  |  `r get.excelled('j4')` | `r get.mastered('j4')` | `r get.partially.mastered('j4')` | `r get.below.expectations('j4')` | `r num.assessed('j4')`
&nbsp;  | (6.5)  |  `r get.excelled('j5')` | `r get.mastered('j5')` | `r get.partially.mastered('j5')` | `r get.below.expectations('j5')` | `r num.assessed('j5')`

## Assessment Data

### COSC 3011: Sotware Design, Danny Radosevich

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 3011: Software Design              | Every other year, starting 2018-19

---

    Performance Indicator (1.2): Analyze at two or more proposed solutions to a 
                                 given problem and select the best solution for 
                                 the given problem
 
    Assessed using weekly stand-up presentations of the design for course project

    51 students were assessed.

    23 students excelled.
    24 students mastered.
    0 students partially mastered.
    4 students were below expectations.

---

    Performance Indicator (2.3): Design the selected solution for a given problem
 
    This was assed via students' submission for their final project. Students were tasked with developing an application throughout the semester, culminating in their submission of a final code base. For this project students were working as a group.

    51 students were assessed.

    23 students excelled.
    24 students mastered.
    2 students partially mastered.
    2 students were below expectations.  

### COSC 3020: Algorithms & Data Structures, Lars Kotthoff

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 3020: Algorithms & Data Structures | Every other year, starting 2016-17

---

    Performance Indicator (1.1): Identify key components and algorithms necessary for a solution 
 
    This was assed using project https://github.com/COSC3020/pancake-sort

    29 students were assessed.

    11 students excelled.
    13 students mastered.
    2 students partially mastered.
    3 students were below expectations.  

---

    Performance Indicator (1.2): Analyze at two or more proposed solutions to a 
                                 given problem and select the best solution for 
                                 the given problem
 
    This was assed using project https://github.com/COSC3020/tsp-comparison

    26 students were assessed.

    8 students excelled.
    1 students mastered.
    3 students partially mastered.
    14 students were below expectations.

---

    Performance Indicator (6.1) Analyze the asymptotic cost of divide-and-conquer algorithms 

    This was assed using project https://github.com/COSC3020/divide-and-conquer-sum

    29 computer science majors were assessed.

    8 students excelled.
    16 mastered.
    4 partially mastered.
    1 were below expectations.

---

    Performance Indicator (6.2) Analyze the asymptotic cost of recursive algorithms 

    This was assed using project https://github.com/COSC3020/recurrence-analysis-mystery

    29 computer science majors were assessed.

    8 students excelled.
    12 mastered.
    6 partially mastered.
    3 were below expectations.

---

    Performance Indicator (6.3) Analyze the asymptotic cost of basic graph algorithms 

    This was assed using project https://github.com/COSC3020/graph-search

    18 computer science majors were assessed.

    7 students excelled.
    5 mastered.
    0 partially mastered.
    6 were below expectations.

---

    Performance Indicator (6.4) Describe the impact of techniques such as caching and dynamic programming on the performance of algorithms 

    This was assed using project https://github.com/COSC3020/dynamic-euler

    27 computer science majors were assessed.

    18 students excelled.
    6 mastered.
    1 partially mastered.
    2 were below expectations.

---

    Performance Indicator (6.5) Understand the difference between polynomial and exponential complexity

    This was assed using project https://github.com/COSC3020/graph-isomorphism

    28 computer science majors were assessed.

    9 students excelled.
    9 mastered.
    6 partially mastered.
    4 were below expectations.

### COSC 3050: Computer Ethics, Robin Hill

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 3050: Computer Ethics              | Every other year, starting 2018-19

---

    Performance Indicator (4.1): Recognize ethical issues involved in a professional setting

 
    Final Exam Q.27: Consider Stewart in Dark UX: to what extent does his ethical quandary depend on the nature of computing (professional ethics) as opposed to business concerns or general ethics?  What does he face that other professionals don't?

    20 students were assessed.

    13 students excelled.
    4 students mastered.
    2 students partially mastered.
    1 students were below expectations.  

---

    Performance Indicator (4.2): Describe current issues in security

    No longer assessed in this class. 

---

    Performance Indicator (4.3): Describe current issues in privacy

    No longer assessed in this class. 

---

    Performance Indicator (4.4): Respect and honor ethics in writing assignments

    Final Exam Q.31:
    We have discussed some standards that developers should follow in coding programs. State one, and use the Categorical Imperative (our version) to justify it.

    20 students were assessed.

    13 students excelled.
    4 students mastered.
    2 students partially mastered.
    1 students were below expectations.  

### COSC 4950/5: Senior Design I & II, Jim Ward

Core Course                             | Assessed
:---------------------------------------|:----------------------------
COSC 4950: Senior Design I              | Every other year, starting 2017-18
COSC 4955: Senior Design II             | Every other year, starting 2017-18

This is the capstone course. Students work in groups ranging from 3 to 5, 
select a project, and create a software system to solve it. The
students flesh out the project ideas, deciding on the important features
and trying to come to terms with project risk.  They decide what technology
to use, and they proceed to implementation.  They also document their
decisions by writing use cases, or other tools as appropriate (e.g., 
story boards for projects that choose to write games).

Classtime is devoted to group work and presentations that updated the 
instructor and the other teams on the status of the project. They also
create a poster presentation of their project and do a final presentation
to a wide audience. The class presentations, poster, and final presentations
are the main tools used for assessment.

    Performance Indicator (2.1): Identify constraints on the design problem

    Via final paper in SD1 and one on one interviews.   

    40 students were assessed.

    37 students excelled.
    3 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.2): Establish acceptance criteria for a solution

    Via final paper in SD1 and one on one interviews.   

    40 students were assessed.

    37 students excelled.
    3 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.3): Design the selected solution for a given problem

    Via final paper in SD1 and one on one interviews. 

    40 students were assessed.

    37 students excelled.
    3 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.4): Implement the designed solution for a given problem

    Via Project notebook in SD2 and one on one interviews.   

    40 students were assessed.

    37 students excelled.
    3 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (2.5): Evaluate the implemented solution

    Via Project notebook in SD2 and one on one interviews.   

    40 students were assessed.

    36 students excelled.
    3 students mastered.
    0 students partially mastered.
    1 students were below expectations.

---

    Performance Indicator (5.1): Listen to other team members

    Using the survey, “What worked well in your team?”

    37 students were assessed.

    30 students excelled.
    7 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.2): Actively discuss team projects, objectives, or challenges with other team members

    Using the survey, “What worked well in your team?”  and “What might you and your team do differently if you had to do it all over again?”

    37 students were assessed.

    30 students excelled.
    7 students mastered.
    0 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.3): Fulfill team duties on time

    Using the survey, “For each of the following, assess YOUR contribution [overall success of project]”, “For each of the following, assess YOUR contribution [overall success of the videos and demos]”, “For each of the following, assess YOUR contribution [to the code base]”, For each of the following, assess YOUR contribution [to the documentation]”.  These questions are then repeated for each team member.

    37 students were assessed.

    29 students excelled.
    6 students mastered.
    2 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.4): Share in the work of the team

    Using the survey:, “For each of the following, assess YOUR contribution [overall success of project]”, “For each of the following, assess YOUR contribution [overall success of the videos and demos]”, “For each of the following, assess YOUR contribution [to the code base]”, For each of the following, assess YOUR contribution [to the documentation]”.  These questions are then repeated for each team member. 

    37 students were assessed.

    29 students excelled.
    6 students mastered.
    2 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (5.5): Research and gather information

    Using the SD1 group project report, and one on one conversations with the groups.

    37 students were assessed.

    29 students excelled.
    5 students mastered.
    3 students partially mastered.
    0 students were below expectations.

---

    Performance Indicator (3.1): Write technical reports

    Via final report in SD1 and Project notebook in SD2.

    37 students were assessed.

    33 students excelled.
    3 students mastered.
    0 students partially mastered.
    1 students were below expectations.

---

    Performance Indicator (3.2): Present technical material to technical peers

    Present at Undergrad Research and Inquiry Days, which is a public event.

    37 students were assessed.

    31 students excelled.
    5 students mastered.
    0 students partially mastered.
    1 students were below expectations.

---

    Performance Indicator (3.3): Present technical material to non-technical visitors

    Present at Undergrad Research and Inquiry Days, which is a public event.

    37 students were assessed.

    31 students excelled.
    5 students mastered.
    0 students partially mastered.
    1 students were below expectations.

